Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.7)} \underline{Drafting Committee: DC90 (\today)}

### 2011-02-24 frame.tex
v0.5 -> v0.6
0.6 - 0.7 removed blue font

\title{
	Beam-Helicity and Charge Asymmetries \\
        in the Bethe-Heitler and DVCS processes on \\
        an Unpolarised Proton Target
  	\underline{Paper Tag: PDVCS (v0.5)}
        \underline{Drafting Committee: DC90 (\today)}
}

\collab{HERMES Collaboration}
\begin{abstract}
Beam\blue{-}helicity and charge asymmetries in the hard exclusive leptoproduction of
real photons from an unpolarised proton target \blue{by} a 27.6\,GeV lepton beam 
are extracted from the HERMES unpolarised data set of 2006-2007 using a
missing-mass event selection technique. The beam-charge asymmetry amplitudes extracted from the new data set are statistically more precise than those extracted from an earlier data set of 1996-2005 previously analysed in the same manner by the collaboration. \blue{Results from both data sets are found to be} compatible with each other. Combined results from these data sets are extracted and are the statistically most precise asymmetry amplitude measurements available in the HERMES kinematic region.
\end{abstract}

>>>>

\title{
	Beam-Helicity and Charge Asymmetries \\
        in the Bethe-Heitler and DVCS processes on \\
        an Unpolarised Proton Target
  	\underline{Paper Tag: PDVCS (v0.7)}
        \underline{Drafting Committee: DC90 (\today)}
}

\collab{HERMES Collaboration}
\begin{abstract}
Beam-helicity and charge asymmetries in the hard exclusive leptoproduction of
real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
are extracted from the HERMES unpolarised data set of 2006-2007 using a
missing-mass event selection technique. The beam-charge asymmetry amplitudes extracted from the new data set are statistically more precise than those extracted from an earlier data set of 1996-2005 previously analysed in the same manner by the collaboration. Results from both data sets are found to be compatible with each other. Combined results from these data sets are extracted and are the statistically most precise asymmetry amplitude measurements available in the HERMES kinematic region.
\end{abstract}
